%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Ray Winkelman's Resume
% Version 1.0 (August 15, 2017)
%
% Author:
% Ray Winkelman
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ray Winkelman} % Your name
\address{Halifax, Nova Scotia, Canada} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{raywinkelman@gmail.com \\ raywinkelman.com} % Your phone number and email


\begin{document}
\begin{rSection}{Synopsis}
A leader in technology and computer program architect with a principal skill set including, but not limited to business development, product ownership, data-driven application development, full-stack web development, server-side program architecture, and relational database design.
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}
%------------------------------------------------

\begin{rSubsection}{Elfster Inc.}{March 2018 - Present}{Senior Software Engineer}{Halifax, NS}

\item[] Senior engineer on a small, remote team supporting and evolving the Elfster.com secret santa and gift exchange platform with 6 million users. Primarily responsible for the evolution of a pragmatic REST API written in ASP.NET Core and our Vue.js client.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{6Joe's Software Inc.}{October 2017 - March 2018}{Lead Software Engineer}{Halifax, NS}

\item[] Hiring manager and director of development of the 6Joe's fantasy sports gaming platform for amateur Golf players and enthusiasts from concept to launch.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Unisys Canada Inc.}{February 2017 - April 2017}{Software Engineer III}{Halifax, NS}

\item[] Worked on a large data migration, system re-architecture, and software development project for the state of Michigan, USA.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{BeyondTrust Software Inc.}{September 2015 - February 2017}{Software Engineer}{Halifax, NS}

\item[] Designed and developed a semantic analysis tool to translate the Transact-SQL programming language into the PL-SQL programming language. Upon completion of a year-long project, merged two vastly diverged versions of the product, using an incrementing Git branching schematic and test cycle.

\end{rSubsection}

%------------------------------------------------


\begin{rSubsection}{HarvestHand Inc.}{May 2015 - September 2015}{Software Developer}{Port Williams, NS}

\item[] Worked with a small team to evolve and support the HavestHand Community Shared Agriculture platform. Delivered several key features including responsive and mobile-first approached themes for farm subdomain websites, and modifications to the ordering and logistics of purchasing produce shares.

\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{TEKsystems Inc.}{April 2014 - August 2014}{Deskside Support}{Waterville, NS}
\item[] Worked with the Deskside Support team to assign, deploy, and service leased computers while executing the "Go7" Windows 7 migration project and reporting the fulfillment of Service Level Agreements between TEKsystems, IBM, and Michelin.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Nova Scotia Community College}{January 2014 - April 2015}{Application Development Tutor}{Halifax, NS}

\item[] Formulated and delivered lessons on advanced object-oriented programming principles, and relational database design to small classes of college students.
\end{rSubsection}


\end{rSection}

\pagebreak
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Nova Scotia Community College, Institute of Technology} \hfill {\em September 2013 - June 2015} \\ 
Information Technology Diploma, Honours \\
Computer Programming Concentration \smallskip \\
Academic Average: 97/100

{\bf Acadia University, Science Program} \hfill {\em September 2011 - June 2013} \\ 
1000$\sim$ and 2000$\sim$ level Advanced Math, Biology, Psychology, and Sociology courses.\\

\end{rSection}


%----------------------------------------------------------------------------------------
%	Voluteering
%----------------------------------------------------------------------------------------

\begin{rSection}{Volunteering}


\begin{rSubsection}{Dalhousie University}{March 2017}{TEDx Volunteer}{Halifax, NS}

\item[] This independently organized series of TED talks addressed the theme "Understanding Uncertainty".\smallskip


\item Welcomed guests and speakers at the entrance, and coordinated ticketing.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Acadia University}{February 2014}{FLL Robot Competition Referee}{Wolfville, NS}

\item[] The Annual Lego Mindstorm Robot Competition is an effort to engage kids in science and technology.\smallskip

\item Observed matches, "called" rule infractions, and determined penalties. 
\item Participated in deliberations regarding robot-related issues and determined official match scores.
\end{rSubsection}

\end{rSection}


%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Skills}

\begin{rSubsection}{}{}{}{}

\item[] \textbf{\textit{Libraries \& Frameworks}}
\item ASP.NET, Codesmith, Cordova, jQuery, Laravel, ServiceStack, Vue.js, Vuetify, Zend
\smallskip

\item[] \textbf{\textit{Programming Languages}}
\item Bash, CSS3, C\#, Go Lang, HTML5, JavaScript/ES6, PHP, Powershell, Transact-SQL
\vspace{3mm}

\item[] \textbf{\textit{Integrated Development Environments}}
\item Atom, Flex Builder, MySQL Workbench, PHPStorm, Stencyl, Visual Studio, VS Code
\vspace{3mm}

\item[] \textbf{\textit{Build Tools \& Package Managers}}
\item Composer, NPM, Nuget, Visual Build Pro, Webpack, Wix
\vspace{3mm}

\item[] \textbf{\textit{Web Servers}}
\item Apache 2, IIS 8, Nginx, Node.js
\vspace{3mm}

\item[] \textbf{\textit{Source Control Systems}}
\item Git Expert, Subversion
\vspace{3mm}

\item[] \textbf{\textit{Operating Systems}}
\item Manjaro/Arch Linux Expert, Windows
\vspace{3mm}

\item[] \textbf{\textit{Virtualization}}
\item VMWare Workstation Pro
\vspace{3mm}

\item[] \textbf{\textit{Cloud Infrastructures}}
\item AWS, Azure, Google App Engine

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
